---
title: "Lab 4 Q10"
author: "Yukun Zhang"
date: "October 01, 2022"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
class: center, middle
# vector add and subtract
we can add two vectors using the + operator

```{r}
c(1, 2, 3) + c(2, 3, 4)
```
we can subtract two vectors using the - operator
```{r}
c(1, 2, 3) - c(2, 3, 4)
```
---
class: center, middle
# vector multiplication and division
we can multiple two vectors using the * operator
```{r}
c(1, 2, 3) * c(2, 3, 4)
```

we can divide two vectors using the / operator
```{r}
c(1, 2, 3) / c(2, 3, 4)
```
---
class: center, middle
# vector add and subtract constant
we can add a vector and a number using the + operator

```{r}
c(1, 2, 3) + 5
```
we can subtract a vector and a number using the - operator
```{r}
c(1, 2, 3) - 5
```
---
class: center, middle
# vector multiplication and division with constant
we can multiple one vector with a number using the * operator
```{r}
c(1, 2, 3) * 5
```

we can divide one vector with a number using the / operator
```{r}
c(1, 2, 3) / 5
```